---
title: "SQL"
output: html_document
---

## Filtering Rows and Columns

If you want to find the specific codes of words for Batting they would use 'colnames(Batting)'. In these examples, SQL is being used. First you need to load these packages:

```{r warning=FALSE, message=FALSE}
library (Lahman)
library (sqldf)
```
# Example

  If we wanted to see the homerun totals for the 1927 Yankees we could write...

```{r}
query<- "SELECT playerID,yearID,teamID,HR FROM Batting
WHERE teamID='NYA' and yearID=1927"
sqldf(query)

```

# Baseball Statistic Examples

Find all instances where the Yankees have hit 40 homeruns or more

```{r}
query<-"SELECT playerID,teamID,yearID,HR FROM Batting WHERE teamID='NYA' and HR>=40"

sqldf(query)
```

Find all instances where a player had more than 40 homeruns but less than 60 strikeouts 

```{r}
query<-"SELECT playerID,teamID,yearID,HR,SO FROM Batting WHERE HR>40 and SO<60"

sqldf(query)
```

Find all instances of the Phillies in the 1970s hitting more than 30 HR 

```{r}
query<-"SELECT playerID,teamID,yearID,HR FROM Batting WHERE teamID='PHI' and yearID>=1970 and yearID<=1979 and HR>30"

sqldf(query)
```

# 'Order By' Examples

Find every instance of a player hitting more than 50 HR but have the players with the most HR at the top of the list

```{r}
query<-"SELECT playerID,teamID,yearID,HR FROM Batting
WHERE HR>50 ORDER BY HR DESC"

sqldf(query)
```

Find all instances of a player striking out less than 10 times. Each player must have at least 400 at-bats (AB). Players with the least amount of strike-outs should be at the top

```{r}
query<-"SELECT playerID,yearID,teamID,SO, AB FROM Batting
WHERE SO<10 and AB>=400
ORDER BY SO"

sqldf(query)
```







